Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-06-20 output/latex/manuscript.tex
latex: fix supplementary tables counter
methods: add data availability and code availability text.

\hypertarget{code-and-data-availability}{%
\subsection{Code and data availability}\label{code-and-data-availability}}

The code and data to reproduce all the analyses in this work are available at \url{https://github.com/greenelab/phenoplier}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-SiobXsoB}{}}%
\CSLLeftMargin{116. }%
\CSLRightInline{Barbeira, A. N. \emph{et al.} \href{https://doi.org/10.1002/gepi.22346}{Fine‐mapping and QTL tissue‐sharing information improves the reliability of causal gene identification}. \emph{Genetic Epidemiology} \textbf{44}, 854--867 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-GPHGnFRN}{}}%
\CSLLeftMargin{117. }%
\CSLRightInline{\emph{\href{https://github.com/hakyimlab/summary-gwas-imputation}{Harmonization and Imputation Overview}}. (hakyimlab, 2022).}

\leavevmode\vadjust pre{\hypertarget{ref-VKYS05n1}{}}%
\CSLLeftMargin{118. }%
\CSLRightInline{Homo sapiens (ID 232177) - BioProject - NCBI. \url{https://www.ncbi.nlm.nih.gov/bioproject/PRJNA232177}.}

@@

\setcounter{figure}{0}

>>>>

\hypertarget{data-availability}{%
\subsection{Data availability}\label{data-availability}}

All the main datasets generated in this study are available at \url{https://doi.org/10.5281/zenodo.8044955}\textsuperscript{\protect\hyperlink{ref-Bf2hvBbr}{116}} and the GitHub repository \url{https://github.com/greenelab/phenoplier}.

The main input datasets used are TWAS from PhenomeXcan\textsuperscript{\protect\hyperlink{ref-lY5ln3dB}{42}} for 4,091 traits and from the Electronic Medical Records and Genomics (eMERGE) network phase III\textsuperscript{\protect\hyperlink{ref-gZAOkumx}{27}} for 309 traits;
transcriptional responses to small molecule perturbations from LINCS L1000\textsuperscript{\protect\hyperlink{ref-F7lIlh2N}{43}} that were further preprocessed and mapped to DrugBank IDs from\textsuperscript{\protect\hyperlink{ref-1DJZvtwP1}{54}};
latent space/gene module models from MultiPLIER\textsuperscript{\protect\hyperlink{ref-14rnBunuZ}{44}}.

\hypertarget{code-availability}{%
\subsection{Code availability}\label{code-availability}}

The code necessary to reproduce all the analyses in this work is available at \url{https://doi.org/10.5281/zenodo.8044955}\textsuperscript{\protect\hyperlink{ref-Bf2hvBbr}{116}} and the GitHub repository \url{https://github.com/greenelab/phenoplier}.

We used Python 3.8 and R 3.6 with several computational packages.
The main Python packages used were: Jupyter Lab (2.2), pandas (1.1), matplotlib (3.3), seaborn (0.11), numpy (1.19), scipy (1.5), scikit-learn (0.23), and umap-learn (0.4).
The main R packages were: Bioconductor (3.10), clusterProfiler (3.14), clustree (0.4), and fgsea (1.17).
We also developed several scripts and notebooks which are published under an open-source license.
We documented all the steps necessary to carry out all the analyses.
We also provide a Docker image to use the same runtime environment we used, and a demo to quickly test the methods on real data.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Bf2hvBbr}{}}%
\CSLLeftMargin{116. }%
\CSLRightInline{Pividori, M. \& Greene, C. \emph{greenelab/phenoplier: Improvements in the source code}. (Zenodo, 2023). doi:\href{https://doi.org/10.5281/zenodo.8044956}{10.5281/zenodo.8044956}.}

\leavevmode\vadjust pre{\hypertarget{ref-SiobXsoB}{}}%
\CSLLeftMargin{117. }%
\CSLRightInline{Barbeira, A. N. \emph{et al.} \href{https://doi.org/10.1002/gepi.22346}{Fine‐mapping and QTL tissue‐sharing information improves the reliability of causal gene identification}. \emph{Genetic Epidemiology} \textbf{44}, 854--867 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-GPHGnFRN}{}}%
\CSLLeftMargin{118. }%
\CSLRightInline{\emph{\href{https://github.com/hakyimlab/summary-gwas-imputation}{Harmonization and Imputation Overview}}. (hakyimlab, 2022).}

\leavevmode\vadjust pre{\hypertarget{ref-VKYS05n1}{}}%
\CSLLeftMargin{119. }%
\CSLRightInline{Homo sapiens (ID 232177) - BioProject - NCBI. \url{https://www.ncbi.nlm.nih.gov/bioproject/PRJNA232177}.}

@@

\setcounter{figure}{0}
\setcounter{table}{0}
